\LARGE \bf Improving Automatic Whiteout++ through Zonal Division of Keyboard

### 2014-10-13 Paper/main.tex
More changes...

\section{Implementation}
In this proposal, we will add a 'keyboard division' feature to classify the four types of error: repeats, roll-on, roll-off, and substitution - specifically the section of the keyboard the key belongs to. We aim to use at least the following three heuristics to divide the keyboard into sections:
\begin{itemize}
\item 3X3 rectangular grid
\item Concentric circles centered at the bottom two corners of the phone to mimic thumb range (Figure 1)
\item Concentric circles with centers as the default position of the thumb when the phone is held (Figure 2)
\end{itemize}

@@

>>>>

\section{Approach}
In this proposal, we will add a 'keyboard division' feature to classify the four types of error: repeats, roll-on, roll-off, and substitution - specifically the section of the keyboard the key belongs to. We aim to use at least the following three heuristics to divide the keyboard into sections:
\begin{itemize}
\item 3X3 rectangular grid
\item Concentric circles centered at the bottom two corners of the phone to mimic thumb range (Figure 1)
\item Concentric circles with centers as the default position of the thumb when the phone is held (Figure 2)
\end{itemize}

@@

\section{Discussion}
